Battling the MAC Bottleneck in IEEE 802.11 Networks

### 2013-01-14 paper.tex
dunno

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Modelling a Decentralized Constraint Satisfaction Solver for Collision-Free Channel Access}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

@@

\begin{abstract}
\boldmath
As the physical layer (PHY) data rates increase and wireless local area network (WLAN) frames become shorter, the medium access control (MAC) overheads account for a larger fraction of the total transmission time.
This problem is known as the MAC bottleneck because it limits the throughput available to regardless no matter how advanced PHY techniques are used.
Current standardization efforts circumvent the problem by using aggregation.
By aggregating multiple network packets in a single MAC layer frame, the MAC overhead per useful network layer bit is reduced.

>>>>

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Battling the MAC Bottleneck in IEEE 802.11 Networks}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

@@

\begin{abstract}
\boldmath
As the physical layer (PHY) data rates increase and wireless local area network (WLAN) frames become shorter, the medium access control (MAC) overheads account for a larger fraction of the total transmission time.
This problem is known as the MAC bottleneck because it limits the throughput available to the user no matter how advanced PHY techniques are used.
Current standardization efforts circumvent the problem by using aggregation.
By aggregating multiple network packets in a single MAC layer frame, the MAC overhead per useful network layer bit is reduced.
